One more attempt on ArXe

### 2015-10-13 exp_results.tex

\begin{figure}[ht]
 \centering
 \includegraphics[width=8.5cm]{pics/figure_oval_1.pdf}
 \caption{
 Outer valence spectra of mixed Ar-Xe clusters, in comparison to the pure species. Panel a) shows the outer valence region of homogeneous Ar and Xe clusters, respectively (see text for details). The two lower panels show the spectra of the mixed species of different size. Sharp lines marked `m' result from photoionization of uncondensed atoms into the Ar 3p$_{1/2,3/2}$ and Xe 5p$_{1/2,3/2}$ final states. Labels in panels b) and c) give the Xe content in the expanding gas mixture, which is lower then the Xe content observed in the heterogeneous clusters. Parts of the spectrum resulting from the Xe inventory of the clusters are shown in blue colour. The photon energy used was 17~eV, apart from the pure Xe cluster spectrum (60 eV).
}
 \label{figure:oval1}
\end{figure}

\begin{figure}[ht]
 \centering
 \includegraphics[width=8.5cm]{pics/figure_oval_2.pdf}
 \caption{
Outer valence spectra of mixed Ar-Xe clusters from gas mixtures with different Xe concentration. See Fig.\ \ref{figure:oval1} and text for details.
}
 \label{figure:oval2}
\end{figure}

>>>>

\begin{figure}[ht]
 \centering
 \includegraphics[width=8.5cm]{pics/figure_oval_1.pdf}
 \caption{
Outer valence photoelectron spectra of mixed Ar-Xe clusters, in comparison to the pure species. Panel a) shows the outer valence region of homogeneous Ar and Xe clusters, respectively (see text for details). The two lower panels show the spectra of the mixed species of different size. Sharp lines marked `m' result from photoionization of uncondensed atoms into the Ar 3p$_{1/2,3/2}$ and Xe 5p$_{1/2,3/2}$ final states. Labels in panels b) and c) give the Xe content in the expanding gas mixture, which is lower then the Xe content observed in the heterogeneous clusters. Parts of the spectrum resulting from the Xe inventory of the clusters are shown in blue colour. The photon energy used was 17~eV, apart from the pure Xe cluster spectrum (60 eV).
}
 \label{figure:oval1}
\end{figure}

\begin{figure}[ht]
 \centering
 \includegraphics[width=8.5cm]{pics/figure_oval_2.pdf}
 \caption{
Outer valence photoelectron spectra of mixed Ar-Xe clusters from gas mixtures with different Xe concentration. See Fig.\ \ref{figure:oval1} and text for details.
}
 \label{figure:oval2}
\end{figure}

\begin{figure}[ht]
 \centering
 \includegraphics[width=8.5cm]{pics/figure_map.pdf}
 \caption{
Photon excited electron-electron coincidence spectra of mixed Ar-Xe clusters in the inner valence region. Panel b): Color-coded map of coincident electron pairs, with high energy electron $e_1$ and low energy electron $e_2$. The kinetic energy of the high energy electron is drawn as binding energy, using the photon energy of $h\nu = 32$~eV. Panel c): Energy spectrum of primary electrons $e_1$, irrespective of the energy of the secondary electron (summation of the coincidence map along horizontal lines). The peak at a binding energy of 28.7~eV pertains to the Ar 3s photoelectron line.  Panel a): Energy spectrum of all secondary (ICD or ETMS) electrons $e_2$ pertaining to the binding energy region marked by two black bars. Intensity is expressed as coincident events/pixel of 20~meV$^2$. See text for details.
}
 \label{figure:map}
\end{figure}
